The Small World Network Effect in Open Source Project Teams \author{Kevin Peterson\\ \small \texttt{pete1968@umn.edu} }

### 2013-11-08 paper/main.tex
Added tables.

\section{Introduction}

\subsection{Hypotheses}

\section{Methods}
\subsection{Collection and Storage}

@@

>>>>

\section{Introduction}
A social network is a graph people and the interactions between them. The dynamics of social networks have proved to be an important research topic for many different areas of study, from academic publication\cite{barabasi2002evolution}, to the success of broadway musicals\cite{uzzi2005collaboration}. In general, a social network is important to understanding how ideas and influence are spread\cite{kempe2003maximizing}, from which we can investigate the best conditions for optimal group perfomance within these networks.

A `small world' network is a social network characterized by high clustering of graph nodes paired with a short average path between nodes \cite{watts1998collective}. Milgram, in is seminal study, found that any two people are linked through a chain of friends and acquaintances on average of 6 people long\cite{milgram1967small}. From these observations, hypotheses can be made as to the efficiency of how knowledge is transfered in these groups\cite{latora2001efficient}. In this work, we investigate the `small world' phenomenon and how it relates to Open Source Project Teams.

\subsection{Hypothesis}

\textit{Open Source Project Teams will perform best at moderate levels of $Q$. This performance, measured by the number of interest their projects generate, will increase as the level of $Q$ increases for the developer graph. This will continue up to an optimal $Q$ value, after which performance will begin to degrade. Thus, the performance curve given $Q$ will be U-shaped, and match Uzzi's findings\cite{uzzi2005collaboration}. }

\section{Methods}

We calcluate the \textit{Clustering Coefficient} (or $CC$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
\[cc = 3 \times \frac{\text{number of triangles}}
                    {\text{number of connected triples}}\]

Also, measuring \textit{Path Length} ($PL$) allows us to gauge how far removed developers in the graph are from one another. For example

\subsection{Collection and Storage}

@@

\input{tables/subgraphs_summary}
